R package partsm 
========================================================

This is the official page for the source code of R package *partsm*, featuring Periodic Autoregressive Time Series Models, available on [CRAN](http://cran.r-project.org/web/packages/partsm/index.html).

For a detailed introduction to periodic autoregressive models, and to the package, look at the [vignette]
(http://cran.r-project.org/web/packages/partsm/vignettes/partsm.pdf).

A quick gallery of partsm
-------------------------


```{r options, echo=FALSE}
opts_chunk$set(warning= FALSE, message=FALSE, fig.align="center", fig.path='figuresREADME/')
```

```{r dataraw, echo=FALSE, fig.height=4, fig.width=10}
library(partsm)
data("gergnp")
lgergnp <- log(gergnp, base=exp(1))
#layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))
plot(gergnp, main="GNP in Germany (1960.1-1990.4)")
#plot(lgergnp, main="Log GNP in Germany (1960.1-1990.4)")
```


### Fit a PAR(2) model with seasonal intercepts.

```{r, echo=FALSE}
detcomp <- list(regular=c(0,0,0), seasonal=c(1,0), regvar=0)
out.par <- fit.ar.par(wts=lgergnp, type="PAR", detcomp=detcomp, p=2)
out.par
```

### Test for periodic variation in the autoregressive parameters

```{r, echo=FALSE}
detcomp <- list(regular=c(0,0,0), seasonal=c(1,0), regvar=0)
    out <- Fpar.test(wts=lgergnp, detcomp=detcomp, p=2)    
out
```

### Test for seasonal heteroskedasticity 

```{r, echo=FALSE}
par2 <- fit.ar.par(wts=lgergnp, type="PAR", p=2, detcomp=detcomp)
Fsh.out <- Fsh.test(res=residuals(par2@lm.par), s=frequency(lgergnp))
Fsh.out
```

### Graphical Representation of the Periodically Differenced Data
```{r plotpdiff, echo=FALSE}
    lgergnp <- log(gergnp, base=exp(1))
    detcomp <- list(regular=c(0,0,0), seasonal=c(1,0), regvar=0)

    ## Fit a PIAR(2) model with seasonal intercepts.
    out.piar <- fit.piar(wts=lgergnp, detcomp=detcomp, p=2)
    plotpdiff(out.piar)
```

